Figures to insert in text

### 2018-04-04 kanerva-answer.tex
trying to reclean...
SDM Fix error from previous commit.

Applying the law of total variance, $\mathbf{V}[\text{cnt}_i | \text{addr}_i = 1] &= \mathbf{V}[2Y_i - \theta] = \mathbf{E}[\mathbf{V}[2Y_i - \theta | \theta]] + \mathbf{V}[\mathbf{E}[2Y_i - \theta | \theta]]$.

>>>>

Applying the law of total variance, $\mathbf{V}[\text{cnt}_i | \text{addr}_i = 1] = \mathbf{V}[2Y_i - \theta] = \mathbf{E}[\mathbf{V}[2Y_i - \theta | \theta]] + \mathbf{V}[\mathbf{E}[2Y_i - \theta | \theta]]$.
